Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-02 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Completed changes, captions and plots

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$, with $L=8$."}

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")
```

@@

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density} shows the empirical densities obtained by applying  the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 8,11\right\}$ and $\mu=1$. Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
Normal QQ plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal QQ-plots for  $n=121$.", fig.width=6, fig.height=5}

@@

The LN distribution in two parameters has the following density function.

@@

Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q-Q plots, P-P plots, as well as empirical and fitted cumulative distribution functions.
They provide qualitative sources confirming that the LN distribution is the most appropriate.

@@

# Guardar los resultados en un archivo .Rdata
save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
```

@@

```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}

@@

```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}

@@

```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$, with  $n=49$, $L=5$ and $\\mu=1$.", fig.width=8, fig.height=6}

@@

```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$, with  $n=49$, $L=5$, $\\mu=1$ and $\\alpha=-3$.", fig.width=8, fig.height=6}

>>>>

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="85%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ when $\\alpha\\to-\\infty$, with $L=8$."}

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$H_{\\Gamma_{\\tiny{SAR}}}$"), vjust = 0.9, hjust = 0.2, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")
```

@@

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density} shows the empirical densities obtained by applying  the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 8,11\right\}$ and $\mu=1$. Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
Normal Q--Q plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$.", fig.width=6, fig.height=5}

@@

The biparametric LN distribution has density:

@@

Figures&nbsp;\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show empirical and fitted density plots, Q--Q plots, P--P plots, as well as empirical and fitted cumulative distribution functions.
They provide qualitative sources that confirm that the LN distribution is the most appropriate distribution.
As expected, both test statistics work well under the null hypothesis.
Under the alternative hypothesis, the P--P plot shows that \(\text{CV}_{\text{MnAD}}\) is more robust than CV, although both statistics suffer from the tail effect caused by the distributed $G_I^0$ data.

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
```

@@

```{r Plot_cv_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with CV data from $\\Gamma_{\\text{SAR}}$ (under the null hypothesis), with $n=49$, $L=5$, and $\\mu=1$.", fig.width=8, fig.height=6}

@@

```{r Plot_cv, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\\mu=1$, and $\\alpha=-3$.", fig.width=8, fig.height=6}

@@

```{r Plot_MnADmedian_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H',  fig.cap="Goodness of fit plots for evaluating the best distribution with $\\text{CV}_{\\text{MnAD}}$ data from $\\Gamma_{\\text{SAR}}$ (under the null hypothesis), with  $n=49$, $L=5$, and $\\mu=1$.", fig.width=8, fig.height=6}

@@

```{r Plot_madmed_gi0_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.pos="hbt",  fig.cap="Goodness of fit plots for evaluating the best distribution with $CV_{\\text{MnAD}}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\\mu=1$, and $\\alpha=-3$.", fig.width=8, fig.height=6}
